---
title: "p8105_hw1_bs3142"
author: "Bingyu Sun"
date: "9/17/2018"
output: html_document
---

# Problem 1
## Create data frame

```{r}
library(tidyverse)
```

```{r}
set.seed(1)

p1_df = tibble(
  random_sample = runif(n = 10, min = 0, max = 5),
  vec_char = c("This", "is", "trying", "to", "answer", "question", "one", "of", "homework", "one"),
  vec_logical = c(random_sample > 2),
  vec_factor = factor(c("blue", "green", "blue", "green", "green", "blue", "blue", "green", "blue", "green"))
)
```

### Means of each variable in my dataframe.

```{r}
mean(p1_df$random_sample)
mean(p1_df$vec_char)
mean(p1_df$vec_logical)
mean(p1_df$vec_factor)
```

Means of random_sample and vec_logical work, whearas means for vec_char and vec_factor do not work. This is because means can only be calculated from numeric values.

#### Convert character, logical, and factor vectors to numeric numbers

Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (show this chunk but not the output).

```{r}
as.numeric(p1_df$vec_char)
as.numeric(p1_df$vec_logical)
as.numeric(p1_df$vec_factor)
```

In a second code chunk, convert your character variable from character to factor to numeric; similarly, convert your factor variable from factor to character to numeric. What happens?

```{r}
vec_char2 <- as.factor(p1_df$vec_char)
as.numeric(vec_char2)

vec_fac2 <- as.character(p1_df$vec_factor)
as.numeric(vec_fac2)
```

# Problem 2
This problem focuses on plotting and the use of inline R code.

## Create data frame

